Synthesizing Symmetric Lenses

### 2018-07-05 papers/SymmetricLenses/main.tex
Stuck at merge left

\subsection{Lens Costs}
Our cost metric is based on the expected amount of information required to
recover a string in one data format from the other. We use the function
$\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ to calculate the expected amount
of information required to recover a string in $\Regex$ from a string in
$\RegexAlt$, synchronized by $\Lens$. We use the function
$\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ to calculate the expected amount
of information required to recover a string in $\RegexAlt$ from a string in
$\Regex$, synchronized by $\Lens$.
\begin{center}
  \begin{tabular}{rcl}
    $\LEntropyOf{\Regex \Given \IdentityLensOf{\Regex}, \Regex}$
    & =
    & 0\\

    $\LEntropyOf{\Regex \Given \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}, \RegexAlt}$
    & =
    & \EntropyOf{\Regex}\\

    $\LEntropyOf{\PRegexStar{\Regex}{\Probability} \Given \IterateLensOf{\Lens}^, \PRegexStar{\RegexAlt}{\ProbabilityAlt}}$
    & =
    & $\frac{\ProbabilityAlt}{1-\ProbabilityAlt}(\LEntropyOf{\Regex \Given \Lens, \RegexAlt})$\\

    $\LEntropyOf{\Regex_1 \Concat \Regex_2 \Given \ConcatLensOf{\Lens_1}{\Lens_2}, \RegexAlt_1 \Concat \RegexAlt_2}$
    & =
    & $\LEntropyOf{\Regex_1 \Given \Lens_1^\leftarrow, \RegexAlt_1} + \LEntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2}$\\

    $\LEntropyOf{\Regex_1 \Concat \Regex_2 \Given \SwapLensOf{\Lens_1}{\Lens_2}, \RegexAlt_2 \Concat \RegexAlt_1}$
    & =
    & $\LEntropyOf{\Regex_1 \Given \Lens_1^\leftarrow, \RegexAlt_1} + \LEntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2}$\\

    $\LEntropyOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability} \Given \OrLensOf{\Lens_1}{\Lens_2}, \PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}}$
    & =
    & $\ProbabilityAlt*(\LEntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt_1}) + (1-\ProbabilityAlt)*(\LEntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2})$\\

    $\LEntropyOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability} \Given \OrLensOf{\Lens_1}{\Lens_2}, \PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}}$
    & =
    & $\ProbabilityAlt*(\LEntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt_1}) + (1-\ProbabilityAlt)*(\LEntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2})$\\

    $\LEntropyOf{\Regex \Given \MergeROf{\Lens_1}{\Lens_2}, \PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}}$
    & =
    & $\ProbabilityAlt*(\LEntropyOf{\Regex \Given \Lens_1, \RegexAlt_1}) + (1-\ProbabilityAlt)*(\LEntropyOf{\Regex \Given \Lens_2, \RegexAlt_2})$\\

    $\LEntropyOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability} \Given \MergeLOf{\Lens_1}{\Lens_2}, \RegexAlt}$
    & =
    & $\Probability*(\LEntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt} - \Log_2(\Probability)) + $\\
    &
    & $(1-\Probability)*(\LEntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt} - \Log_2(1 - \Probability))$\\

    $\LEntropyOf{\RegexAlt \Given \InvertOf{\Lens}, \Regex}$
    & =
    & $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$\\
  \end{tabular}
\end{center}
$\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ is defined symmetrically.  These
functions calculate the expected number of bits to recover one data format from
a synchronized string in the other format.
The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\LEntropyOf{\Regex \Given \Lens, \RegexAlt} + \REntropyOf{\RegexAlt \Given
  \Lens, \Regex}$ is the
sum of recovering the left format from the right, and the right from the left.
We have proven theorems demonstrating the calculated entropy corresponds to the
actual conditional entropy to recover the data.\bcp{Again, they should be
  included.}

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem}

@@

Since $S$ is unambiguous, then $S_1$ and $S_2$ are also unambiguous, and every $s \in \mathcal{L}(S_1 \; |_p \; S_2)$ is either in $\mathcal{L}(S_1)$ or in $\mathcal{L}(S_2)$. By the induction hypothesis, $H(\mathcal{L}(S_1)) = \mathbb{H}(S_1)$ and $H(\mathcal{L}(S_2)) = \mathbb{H}(S_2)$. Then
\begin{align*}
H(\mathcal{L}(S_1 \; |_p \; S_2)) &= -\sum_{s \in \mathcal{L}(S_1)}(p * P_{S_1}(s))\log_2 (p * P_{S_1}(s)) - \sum_{s \in \mathcal{L}(S_2)}((1-p) * P_{S_2}(s))\log_2 ((1-p) * P_{S_2}(s))\\
&=- p\sum_{s \in \mathcal{L}(S_1)}P_{S_1}(s)(\log_2 p + \log_2 P_{S_1}(s)) - (1-p)\sum_{s \in \mathcal{L}(S_2)}P_{S_2}(s)(\log_2 (1-p) + \log_2 P_{S_2}(s))\\
&= p * (\log_2 p +  H(\mathcal{L}(S_1))) + (1-p) * ( \log_2 (1-p) + H(\mathcal{L}(S_2)))\\
&= p * (\log_2 p +  \mathbb{H}(S_1)) + (1-p) * ( \log_2 (1-p) + \mathbb{H}(S_2))\\
\end{align*}
\end{enumerate}
\end{proof}
\end{document}

>>>>

\subsection{Lens Costs}
Our cost metric is based on the expected amount of information required to
recover a string in one data format from the other. We use the function
$\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ to calculate the expected amount
of information required to recover a string in $\Regex$ from a string in
$\RegexAlt$, synchronized by $\Lens$. We use the function
$\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ to calculate the expected amount
of information required to recover a string in $\RegexAlt$ from a string in
$\Regex$, synchronized by $\Lens$.
\begin{center}
  \begin{tabular}{rcl}
    $\REntropyOf{\Regex \Given \IdentityLensOf{\Regex}, \Regex}$
    & =
    & 0\\

    $\REntropyOf{\Regex \Given \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}, \RegexAlt}$
    & =
    & \EntropyOf{\RegexAlt}\\

    $\REntropyOf{\PRegexStar{\Regex}{\Probability} \Given \IterateLensOf{\Lens}^, \PRegexStar{\RegexAlt}{\ProbabilityAlt}}$
    & =
    & $\frac{\Probability}{1-\Probability}(\REntropyOf{\Regex \Given \Lens, \RegexAlt})$\\

    $\REntropyOf{\Regex_1 \Concat \Regex_2 \Given \ConcatLensOf{\Lens_1}{\Lens_2}, \RegexAlt_1 \Concat \RegexAlt_2}$
    & =
    & $\REntropyOf{\Regex_1 \Given \Lens_1^\leftarrow, \RegexAlt_1} + \REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2}$\\

    $\REntropyOf{\Regex_1 \Concat \Regex_2 \Given \SwapLensOf{\Lens_1}{\Lens_2}, \RegexAlt_2 \Concat \RegexAlt_1}$
    & =
    & $\REntropyOf{\Regex_1 \Given \Lens_1^\leftarrow, \RegexAlt_1} + \REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2}$\\

    $\REntropyOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability} \Given \OrLensOf{\Lens_1}{\Lens_2}, \PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}}$
    & =
    & $\Probability*(\REntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt_1} ) + (1-\Probability)*(\REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2})$\\

    $\REntropyOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability} \Given \MergeROf{\Lens_1}{\Lens_2}, \RegexAlt}$
    & =
    & $\Probability*(\REntropyOf{\Regex \Given \Lens_1, \RegexAlt_1}) + (1-\Probability)*(\REntropyOf{\Regex \Given \Lens_2, \RegexAlt_2})$\\

    $\REntropyOf{\Regex \Given \MergeLOf{\Lens_1}{\Lens_2}, \PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}}$
    & =
    & $\ProbabilityAlt*(\REntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt} - \Log_2(\ProbabilityAlt)) + $\\
    &
    & $(1-\ProbabilityAlt)*(\REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt} - \Log_2(1 - \ProbabilityAlt))$\\

    $\REntropyOf{\RegexAlt \Given \InvertOf{\Lens}, \Regex}$
    & =
    & $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$\\
  \end{tabular}
\end{center}
$\LEntropyOf{\RegexAlt \Given \Lens, \Regex}$ is defined symmetrically.  These
functions calculate the expected number of bits to recover one data format from
a synchronized string in the other format.
The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\LEntropyOf{\Regex \Given \Lens, \RegexAlt} + \REntropyOf{\RegexAlt \Given
  \Lens, \Regex}$ is the
sum of recovering the left format from the right, and the right from the left.
We have proven theorems demonstrating the calculated entropy corresponds to the
actual conditional entropy to recover the data.\bcp{Again, they should be
  included.}

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem}

@@

Since $S$ is unambiguous, then $S_1$ and $S_2$ are also unambiguous, and every $s \in \mathcal{L}(S_1 \; |_p \; S_2)$ is either in $\mathcal{L}(S_1)$ or in $\mathcal{L}(S_2)$. By the induction hypothesis, $H(\mathcal{L}(S_1)) = \mathbb{H}(S_1)$ and $H(\mathcal{L}(S_2)) = \mathbb{H}(S_2)$. Then
\begin{align*}
H(\mathcal{L}(S_1 \; |_p \; S_2)) &= -\sum_{s \in \mathcal{L}(S_1)}(p * P_{S_1}(s))\log_2 (p * P_{S_1}(s)) - \sum_{s \in \mathcal{L}(S_2)}((1-p) * P_{S_2}(s))\log_2 ((1-p) * P_{S_2}(s))\\
&=- p\sum_{s \in \mathcal{L}(S_1)}P_{S_1}(s)(\log_2 p + \log_2 P_{S_1}(s)) - (1-p)\sum_{s \in \mathcal{L}(S_2)}P_{S_2}(s)(\log_2 (1-p) + \log_2 P_{S_2}(s))\\
&= p * (\log_2 p +  H(\mathcal{L}(S_1))) + (1-p) * ( \log_2 (1-p) + H(\mathcal{L}(S_2)))\\
&= p * (\log_2 p +  \mathbb{H}(S_1)) + (1-p) * ( \log_2 (1-p) + \mathbb{H}(S_2))\\
\end{align*}
\end{enumerate}
\end{proof}
\begin{theorem*}
  Let $\Lens$ be an asymmetric lens. $\Lens$ is also a simple symmetric lens,
  where
  \begin{center}
    \begin{tabular}{rcl}
      $\Lens.\CreateROf{x}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\CreateLOf{y}$ & $=$ & $\Lens.create \App y$\\
      $\Lens.\PutROf{x}{y}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\PutLOf{y}{x}$ & $=$ & $\Lens.put \App y \App x$
    \end{tabular}
  \end{center}
\end{theorem*}
\begin{proof}
Let $\ell$ be an asymmetric lens. Then $\ell$ satisfies the following laws:
\begin{align*}
\ell.\get \; (\ell.\pput \; v \; s) &= v \tag{PUTGET}\\
\ell.\pput \; (\ell.\get \; s) \; s&= s \tag{GETPUT}\\
\ell.\get \; (\ell.\pput \; v \; s) &= v \tag{CREATGET}
\end{align*}
Define the simple symmetric lens $\lceil \ell \rceil$ by 
\begin{align*}
\lceil \ell \rceil.\CreateROf{s} &= \ell.\get \; s\\
\lceil \ell \rceil.\CreateLOf{v} &= \ell.\create \; v\\
\lceil \ell \rceil.\PutROf{s}{v} &= \ell.\get \; s\\
\lceil \ell \rceil.\PutLOf{v}{s} &= \ell.\pput \; v \; s\\
\end{align*}
We now show that $\lceil \ell \rceil$ satisfies the simple symmetric lens laws:
\begin{align*}
\lceil \ell \rceil.\PutLOf{(\lceil \ell \rceil.\CreateROf{s})}{s} &= \ell.\pput \; (\ell.\get \; s) \; s = s\\
\lceil \ell \rceil.\PutROf{(\lceil \ell \rceil.\CreateLOf{v})}{v} &= \ell.\get \; (\ell.\create \; v) = v\\
\lceil \ell \rceil.\PutLOf{(\lceil \ell \rceil.\PutROf{s}{v})}{s} &= \ell.\pput \; (\ell.\get) \; s = s\\
\lceil \ell \rceil.\PutROf{(\lceil \ell \rceil.\PutLOf{v}{s})}{v} &= \ell.\get \; (\ell.\pput \; v \; s) = v
\end{align*}
\end{proof}

\begin{theorem*}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem*}
\begin{proof}
Given $s \in S$, let $V_{\ell}(s) = \{t \in \mathcal{L}(T) \; | \; \ell.\PutROf{s}{t} = t\}$. We want to show that
$$\sum_{s \in \mathcal{L}(S)}P_{\mathcal{L}(S)}(s)H(V_{\ell}(s)) = \mathbb{H}^{\rightarrow}(S \; | \; \ell, T)$$
We proceed by induction over $\ell$. 
\begin{enumerate}
\item
($\ell = \IdentityLensOf{S}$)

Observe that $V_{\IdentityLensOf{S}}(s) = \{t \in \mathcal{L}(S) \; | \; \IdentityLensOf{S}.\ell.\PutROf{s}{t} = t\} = \{t \in \mathcal{L}(S) \; | \; t = s\} = \{s\}$.

Consequently, $H(V_{\IdentityLensOf{S}}(s)) = H(\{s\}) = 0$, from which it follows that 
$$\sum_{s \in \mathcal{L}(S)} P_{\mathcal{L}(S)}(s) * H(V_{\IdentityLensOf{S}}(s)) = 0 = \mathbb{H}^{\rightarrow}(S \; | \; \IdentityLensOf{S}, T)$$
\item
($\ell = \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}$)

Observe that 
$$V_{\DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}}(s) = \{t \in \mathcal{L}(T) \; | \; \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}.\PutROf{s}{t} = t\} = \{t \in \mathcal{L}(T) \; | \; t = t\} = \mathcal{L}(T)$$
Consequently
$$\sum_{s \in \mathcal{L}(S)}P_{S}(s)H(V_{\DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}}(s)) = \sum_{s \in \mathcal{L}(S)}P_{S}(s)H(\mathcal{L}(T)) = H(\mathcal{L}(T)) = \mathbb{H}(T) = \mathbb{H}^{\rightarrow}(S \; | \; \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}, T)$$
\item
($\ell = \IterateLensOf{\Lens} : S^{*p} \Leftrightarrow T^{*q}$)

Observe that 
\begin{align*}
V_{\IterateLensOf{\Lens}}(s_1 \cdot \ldots \cdot s_n) &= \{t_1 \cdot \ldots \cdot t_m \; | \; \IterateLensOf{\Lens}.\PutROf{(s_1 \cdot \ldots \cdot s_n) }{(t_1 \cdot \ldots \cdot t_m)} = t_1 \cdot \ldots \cdot t_m\}\\
&= \{t_1 \cdot \ldots \cdot t_n \; | \; \ell.\PutROf{s_i}{t_i} = t_i \text{ for }1 \leq i \leq n\}\\
&= V_{\ell}(s_1) \cdot \ldots \cdot V_{\ell}(s_n)
\end{align*}
Consequently
\begin{align*}
\sum_{s \in \mathcal{L}(S^{*p})}P_{S^{*p}}(s) H(V_{\IterateLensOf{\Lens}}(s))
&= (1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_n)\\s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i) H(V_{\ell}(s_1) \cdot \ldots \cdot V_{\ell}(s_n))\\
&= (1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_n)\\s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i) \left(\sum_{j=1}^n H(V_{\ell}(s_j)) \right)\\
&= (1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots s_{n-1}) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^{n-1}P_S(s_i) \sum_{s_n} P_S(s_n) \left(\sum_{j=1}^n H(V_{\ell}(s_j)) \right)
\end{align*}
We focus on the term $\sum_{s_n} P_S(s_n) \sum_{j=1}^n H(V_{\ell}(s_j))$:
\begin{align*}
\sum_{s_n} P_S(s_n) \sum_{j=1}^n H(V_{\ell}(s_j)) &= \sum_{s_n} P_S(s_n)H(V_{\ell}(s_n)) + P_S(s_n) \sum_{j=1}^{n-1} H(V_{\ell}(s_j))\\
&= \mathbb{H}^{\rightarrow}(S \; | \; \ell, T) + \sum_{j=1}^{n-1}H(V_{\ell}(s_j))
\end{align*}
Consequently,
\begin{align*}
\sum_{s \in \mathcal{L}(S^{*p})}P_{S^{*p}}(s) H(V_{\IterateLensOf{\Lens}}(s))
&= (1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots s_{n-1}) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^{n-1}P_S(s_i) \left( \mathbb{H}^{\rightarrow}(S \; | \; \ell, T) + \sum_{j=1}^{n-1}H(V_{\ell}(s_j))\right)\\
&= (1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_{n-1})\\s_i \in \mathcal{L}(S)}} \prod_{i=1}^{n-1}P_S(s_i) \mathbb{H}^{\rightarrow}(S \; | \; \ell, T)\\
&+(1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_{n-1}) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^{n-1}P_S(s_i) \left(\sum_{j=1}^{n-1}H(V_{\ell}(s_j))\right)\\
&= \mathbb{H}^{\rightarrow}(S \; | \; \ell, T) * (1-p)\sum_n p^n \\
&+(1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_{n-1}) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^{n-1}P_S(s_i) \left(\sum_{j=1}^{n-1}H(V_{\ell}(s_j))\right)
\end{align*}
Unrolling the term 
$$\sum_{\substack{(s_1, \ldots, s_{n-1}) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^{n-1}P_S(s_i) \left(\sum_{j=1}^{n-1}H(V_{\ell}(s_j))\right)$$ 
$(n-1)$ more times gives
$$\sum_{s \in \mathcal{L}(S^{*p})}P_{S^{*p}}(s) H(V_{\IterateLensOf{\Lens}}(s))
= \mathbb{H}^{\rightarrow}(S \; | \; \ell, T) * (1-p)\sum_n n * p^n  = \frac{p}{1-p} * \mathbb{H}^{\rightarrow}(S \; | \; \ell, T)$$
which is what we wanted to show.
\item
($S = \ConcatLensOf{\Lens_1}{\Lens_2}$)

Observe that 
\begin{align*}
V_{ \ConcatLensOf{\Lens_1}{\Lens_2}}(s_1 \cdot s_2) &= \{t_1 \cdot t_2 \in \mathcal{L}(T_1 \cdot T_2) \; | \;  \ConcatLensOf{\Lens_1}{\Lens_2}.\PutROf{(s_1 \cdot s_2)}{(t_1 \cdot t_2)} = t_1 \cdot t_2\}\\
&= \{t_1 \cdot t_2 \in \mathcal{L}(T_1 \cdot T_2) \; | \;  \ell_1.\PutROf{s_1}{t_1 } = t_1  \text{ and } \ell_2.\PutROf{t_2}{t_2} = t_2\}\\
&= V_{\ell_1}(s_1) \cdot V_{\ell_2}(s_2)
\end{align*}
Consequently,
\begin{align*}
&\sum_{s \in \mathcal{L}(S_1 \cdot S_2)}P_{S_1 \cdot S_2}(s) H(V_{\ConcatLensOf{\Lens_1}{\Lens_2}}(s))\\
&= \sum_{s_1 \in \mathcal{L}(s_1)} P_{S_1}(s_1)\sum_{s_2 \in \mathcal{L}(s_2)}P_{S_2}(s_2)(H(V_{\ell_1}(s_1)) + H(V_{\ell_2}(s_2)))\\
&= \sum_{s_1 \in \mathcal{L}(s_1)} P_{S_1}(s_1)\sum_{s_2 \in \mathcal{L}(s_2)}P_{S_2}(s_2)H(V_{\ell_1}(s_1)) + \sum_{s_1 \in \mathcal{L}(s_1)} P_{S_1}(s_1)\sum_{s_2 \in \mathcal{L}(s_2)}P_{S_2}(s_2)H(V_{\ell_2}(s_2))\\
&= \mathbb{H}^{\rightarrow}(S_1 \; | \; \ell_1, T_1) + \mathbb{H}^{\rightarrow}(S_2 \; | \; \ell_2, T_2)
\end{align*}
\item
($S = \SwapLensOf{\Lens_1}{\Lens_2}$)

Similar to the previous case.
\item
($S = \OrLensOf{\Lens_1}{\Lens_2}$)

Observe that 
$$
V_{ \OrLensOf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \OrLensOf{\Lens_1}{\Lens_2}.\ell.\PutROf{s}{t} = t\}
$$
If $s \in \mathcal{L}(S_1)$, then
$$
V_{ \OrLensOf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \ell_1.\PutROf{s}{t} = t\} = V_{\ell_1}(s)
$$
while if $s \in \mathcal{L}(S_2)$, then
$$
V_{ \OrLensOf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \ell_2.\PutROf{s}{t} = t\} = V_{\ell_2}(s)
$$
Consequently,
\begin{align*}
&\sum_{s \in \mathcal{L}(S_1 \; |_p \; S_2)}P_{S_1 \; |_p \; S_2}(s) H(V_{\OrLensOf{\Lens_1}{\Lens_2}}(s))\\
&= p * \sum_{s \in \mathcal{L}(S_1)}P_{S_1}(s) H(V_{\ell_1}(s)) + (1-p) * \sum_{s \in \mathcal{L}(S_2)}P_{S_2}(s) H(V_{\ell_2}(s))\\
&= p * (\mathbb{H}^{\rightarrow}(S_1 \; | \; \ell_1,T_1)) + (1-p) * (\mathbb{H}^{\rightarrow}(S_2 \; | \; \ell_2,T_2))
\end{align*}
\item
($S = \MergeROf{\Lens_1}{\Lens_2}$)

Observe that 
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \MergeROf{\Lens_1}{\Lens_2}.\ell.\PutROf{s}{t} = t\}
$$
If $s \in \mathcal{L}(S_1)$, then
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \ell_1.\PutROf{s}{t} = t\} = V_{\ell_1}(s)
$$
while if $s \in \mathcal{L}(S_2)$, then
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \ell_2.\PutROf{s}{t} = t\} = V_{\ell_2}(s)
$$
Consequently,
\begin{align*}
&\sum_{s \in \mathcal{L}(S_1 \; |_p \; S_2)}P_{S_1 \; |_p \; S_2}(s) H(V_{\MergeROf{\Lens_1}{\Lens_2}}(s))\\
&= p * \sum_{s \in \mathcal{L}(S_1)}P_{S_1}(s) H(V_{\ell_1}(s)) + (1-p) * \sum_{s \in \mathcal{L}(S_2)}P_{S_2}(s) H(V_{\ell_2}(s))\\
&= p * (\mathbb{H}^{\rightarrow}(S_1 \; | \; \ell_1,T_1) ) + (1-p) * (\mathbb{H}^{\rightarrow}(S_2 \; | \; \ell_2,T_2) )
\end{align*}
\item
($S = \MergeLOf{\Lens_1}{\Lens_2}$)
